New and simplified manual controls for projection and slice tours, with application to exploring classification boundaries in high dimensions

### 2023-01-18 paper/paper.Rmd
removed references to color

Both models have some overlap at the center for the thin slice based on $A_1$ (despite the small value for $h$). The second slice (based on $A_2$) mostly resolves this overlap and reveals the primary differences between the models. The boundary between Adelie (blue) and Chinstrap (yellow) is very similar for both models. The boundary between Chinstrap and Gentoo (green) is where they differ.

@@

We start by a comparison of the two models and the data distribution shifting to $\mathbf{c}^{+}$, thus the slice is localized towards high values of bill depth in Figure \ref{slice1p}. We can see that all three slices (the two models and the data) contain almost no points from the third class (green, Gentoo), and that the decision boundary between the two models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center in the positive direction of bill depth produces regions that have no Gentoo (green). The two models have similar boundaries except that the RF is more of a step function.}
\label{slice1p}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_m_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_data.png}}
\caption{Shifting the slice center in the negative direction of bill depth produces regions that are mostly Gentoo (green). The two models have very different boundaries: the nonlinear potential of RF can be seen here where still some subspaces would predict to be Adelie and Chinstrap.}
\label{slice1m}
\end{figure*}

A more interesting comparison is found for $\mathbf{c}^{-}$, thus the slice localized towards low values of bill depth, shown in Figure \ref{slice1m}. The RF model (left) predicts all three species within this slice, with an interesting boundary for the third class (green, Gentoo). On the other hand the LDA model (middle) predominantly predicts the third class within the slice, this appears to be enforced through the linear structure of the model. Looking finally at the thick slice through the data we see that there are primarily observations from this class within the slice we can conclude that the two models have filled in the "empty" space (where we do not have any training observations) in very different ways and according to what we might expect given the model structure.

>>>>

Both models have some overlap at the center for the thin slice based on $A_1$ (despite the small value for $h$). The second slice (based on $A_2$) mostly resolves this overlap and reveals the primary differences between the models. The boundary between Adelie and Chinstrap  is very similar for both models. The boundary between Chinstrap and Gentoo is where they differ.

@@

We start by a comparison of the two models and the data distribution shifting to $\mathbf{c}^{+}$, thus the slice is localized towards high values of bill depth in Figure \ref{slice1p}. We can see that all three slices (the two models and the data) contain almost no points from the third class (Gentoo), and that the decision boundary between the two models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center in the positive direction of bill depth produces regions that have no Gentoo. The two models have similar boundaries except that the RF is more of a step function.}
\label{slice1p}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_m_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_data.png}}
\caption{Shifting the slice center in the negative direction of bill depth produces regions that are mostly Gentoo. The two models have very different boundaries: the nonlinear potential of RF can be seen here where still some subspaces would predict to be Adelie and Chinstrap.}
\label{slice1m}
\end{figure*}

A more interesting comparison is found for $\mathbf{c}^{-}$, thus the slice localized towards low values of bill depth, shown in Figure \ref{slice1m}. The RF model (left) predicts all three species within this slice, with an interesting boundary for the third class (Gentoo). On the other hand the LDA model (middle) predominantly predicts the third class within the slice, this appears to be enforced through the linear structure of the model. Looking finally at the thick slice through the data we see that there are primarily observations from this class within the slice we can conclude that the two models have filled in the "empty" space (where we do not have any training observations) in very different ways and according to what we might expect given the model structure.

### 2023-01-18 paper/paper.tex
removed references to color

Both models have some overlap at the center for the thin slice based on
\(A_1\) (despite the small value for \(h\)). The second slice (based on
\(A_2\)) mostly resolves this overlap and reveals the primary
differences between the models. The boundary between Adelie (blue) and
Chinstrap (yellow) is very similar for both models. The boundary between
Chinstrap and Gentoo (green) is where they differ.

@@

We start by a comparison of the two models and the data distribution
shifting to \(\mathbf{c}^{+}\), thus the slice is localized towards high
values of bill depth in Figure \ref{slice1p}. We can see that all three
slices (the two models and the data) contain almost no points from the
third class (green, Gentoo), and that the decision boundary between the
two models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center in the positive direction of bill depth produces regions that have no Gentoo (green). The two models have similar boundaries except that the RF is more of a step function.}
\label{slice1p}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_m_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_data.png}}
\caption{Shifting the slice center in the negative direction of bill depth produces regions that are mostly Gentoo (green). The two models have very different boundaries: the nonlinear potential of RF can be seen here where still some subspaces would predict to be Adelie and Chinstrap.}
\label{slice1m}
\end{figure*}

A more interesting comparison is found for \(\mathbf{c}^{-}\), thus the
slice localized towards low values of bill depth, shown in Figure
\ref{slice1m}. The RF model (left) predicts all three species within
this slice, with an interesting boundary for the third class (green,
Gentoo). On the other hand the LDA model (middle) predominantly predicts
the third class within the slice, this appears to be enforced through
the linear structure of the model. Looking finally at the thick slice
through the data we see that there are primarily observations from this
class within the slice we can conclude that the two models have filled
in the ``empty'' space (where we do not have any training observations)
in very different ways and according to what we might expect given the
model structure.

>>>>

Both models have some overlap at the center for the thin slice based on
\(A_1\) (despite the small value for \(h\)). The second slice (based on
\(A_2\)) mostly resolves this overlap and reveals the primary
differences between the models. The boundary between Adelie and
Chinstrap is very similar for both models. The boundary between
Chinstrap and Gentoo is where they differ.

@@

We start by a comparison of the two models and the data distribution
shifting to \(\mathbf{c}^{+}\), thus the slice is localized towards high
values of bill depth in Figure \ref{slice1p}. We can see that all three
slices (the two models and the data) contain almost no points from the
third class (Gentoo), and that the decision boundary between the two
models is very similar.

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_p_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_p_data.png}}
\caption{Shifting the slice center in the positive direction of bill depth produces regions that have no Gentoo. The two models have similar boundaries except that the RF is more of a step function.}
\label{slice1p}
\end{figure*}

\begin{figure*}[ht]
\centerline{\includegraphics[width=0.32\textwidth]{figures/slice1_m_rf.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_lda.png}
\includegraphics[width=0.32\textwidth]{figures/slice1_m_data.png}}
\caption{Shifting the slice center in the negative direction of bill depth produces regions that are mostly Gentoo. The two models have very different boundaries: the nonlinear potential of RF can be seen here where still some subspaces would predict to be Adelie and Chinstrap.}
\label{slice1m}
\end{figure*}

A more interesting comparison is found for \(\mathbf{c}^{-}\), thus the
slice localized towards low values of bill depth, shown in Figure
\ref{slice1m}. The RF model (left) predicts all three species within
this slice, with an interesting boundary for the third class (Gentoo).
On the other hand the LDA model (middle) predominantly predicts the
third class within the slice, this appears to be enforced through the
linear structure of the model. Looking finally at the thick slice
through the data we see that there are primarily observations from this
class within the slice we can conclude that the two models have filled
in the ``empty'' space (where we do not have any training observations)
in very different ways and according to what we might expect given the
model structure.
